\documentclass[12pt,a4paper]{article}

% --- Packages ---
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{mathptmx}
\usepackage{amsmath,amssymb}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{longtable}
\usepackage{geometry}
\usepackage{setspace}
\usepackage{hyperref}
\usepackage{natbib}
\usepackage{graphicx}
\usepackage{pdflscape}
\usepackage{caption}
\usepackage{float}
\usepackage{array}
\usepackage{multirow}
\usepackage{threeparttable}

\geometry{margin=1in}
\setstretch{1.44}
\emergencystretch=3em
\tolerance=1000
\hypersetup{colorlinks=true, linkcolor=blue, citecolor=blue, urlcolor=blue}

% --- Custom column types ---
\newcolumntype{L}[1]{>{\raggedright\arraybackslash}p{#1}}
\newcolumntype{C}[1]{>{\centering\arraybackslash}p{#1}}
\newcolumntype{R}[1]{>{\raggedleft\arraybackslash}p{#1}}

\begin{document}

% ============================================================
% TITLE
% ============================================================
\begin{titlepage}
\null\vfill
\begin{center}
{\LARGE \textbf{Uncertainty in Earnings Calls and Takeover Hazards}} \\[1.5em]
{\large Sina Soleimanipour} \\[0.5em]
{\normalsize Telfer School of Management, University of Ottawa} \\[1.5em]
{\normalsize Thesis Advisors: Dr.\ Ali Akyol \quad Dr.\ Harshit Rajaiya} \\[1em]
{\normalsize Draft — \today}
\end{center}
\vfill
\end{titlepage}

% ============================================================
% I. ABSTRACT
% ============================================================
\section{Abstract}
\label{sec:abstract}

[Placeholder for abstract.]

% ============================================================
% II. CONCEPTUAL FRAMEWORK AND METHODOLOGY
% ============================================================
\section{Conceptual Framework and Methodology}
\label{sec:framework}

\subsection{Literature Review and Hypothesis Development}
\label{sec:litreview}

[Placeholder for literature review.]

Based on the foregoing, we formulate two hypotheses:

\begin{quote}
\textbf{H1.} \textit{Linguistic uncertainty in earnings calls increases post-call stock market illiquidity.}
\end{quote}

\begin{quote}
\textbf{H2.} \textit{Linguistic uncertainty in earnings calls increases takeover likelihood, particularly for uninvited (hostile) bids.}
\end{quote}

\subsection{Methodology}
\label{sec:methodology}

We employ three estimation frameworks, each suited to the dependent variable and data structure of the hypothesis under study.

\paragraph{Panel Fixed-Effects OLS (H0.3).}
To replicate and extend Dzielinski et al.\ (2017), we estimate OLS regressions of QA-section uncertainty on presentation-section uncertainty, analyst uncertainty, negative sentiment, and financial controls. Each model includes CEO fixed effects and year fixed effects, both included as indicator variables. Standard errors are clustered at the CEO level. We estimate four specifications: a Manager variant and a CEO variant, each in a Baseline form (replicating the original study's control set: stock return, market return, EPS growth, and earnings surprise decile) and an Extended form that adds firm size, book-to-market, leverage, ROA, current ratio, R\&D intensity, and stock return volatility.

\paragraph{Panel Fixed-Effects Regression (H7, H14).}
To test whether linguistic uncertainty in earnings calls affects stock market illiquidity, we estimate panel regressions with firm and time fixed effects using the \textit{linearmodels} PanelOLS estimator. Standard errors are clustered at the firm level. For H7 (Amihud illiquidity change), the time fixed effect is a fiscal-quarter integer; for H14 (bid-ask spread change), it is a year--quarter index defined as $\text{year} \times 4 + \text{quarter}$. Both H7 and H14 use an event-study design with short event windows ($\pm$3 trading days around the call). Control variables include firm size, leverage, ROA, Tobin's Q, pre-call Amihud illiquidity, and two linguistic controls (negative sentiment and analyst uncertainty) for H7, or firm size, stock price, share turnover, return volatility, pre-call spread level, and absolute earnings surprise decile for H14. We estimate raw linguistic uncertainty variants (CEO QA, CEO presentation, manager QA, manager presentation) as well as clarity-residual variants that partial out the linguistic determinants of uncertainty identified in the H0.3 replication.

\paragraph{Cox Proportional Hazards Models (H9).}
To examine whether speech uncertainty predicts takeover likelihood, we estimate Cox proportional hazards models with time-varying covariates in counting-process (start, stop) format. We consider three event types: all takeovers, uninvited (hostile) takeovers, and friendly takeovers. Uninvited and friendly events are modeled as cause-specific hazards, treating competing event types as censored. Controls include firm size, book-to-market, leverage, ROA, and cash holdings. Standard errors are robust sandwich estimators, as is the default in the \textit{lifelines} CoxTimeVaryingFitter; we note that these are not clustered at the firm level. We report hazard ratios for the main (sparse) specification across three clarity variants: the CEO clarity score, the CEO clarity residual, and the manager clarity residual.

% ============================================================
% III. MAIN EMPIRICAL ANALYSES
% ============================================================
\section{Main Empirical Analyses}
\label{sec:main}

\subsection{Data Sources}
\label{sec:data}

Our data draw on several standard sources accessed through the Wharton Research Data Services (WRDS) platform. Quarterly accounting data (total assets, book equity, leverage, ROA, current ratio, R\&D expenditure, cash holdings) come from \textbf{Compustat Quarterly}. Daily stock-level data (prices, returns, trading volume, shares outstanding) come from \textbf{CRSP Daily}. We obtain individual analyst earnings forecasts and actuals from \textbf{IBES Detail}, which we use to construct earnings surprise measures. The link between Compustat and CRSP identifiers is established through the \textbf{CRSP--Compustat Merged (CCM)} linktable. CEO identities and tenure information are obtained from \textbf{Execucomp}, which provides the executive identifier used to construct CEO fixed effects and enforce the minimum-five-calls filter in CEO-level specifications. Execucomp covers firms in the S\&P~1500 index (S\&P~500, S\&P~MidCap~400, and S\&P~SmallCap~600).

The primary text data consist of \textbf{earnings call transcripts from Capital IQ} spanning 2002--2018. From each transcript, we extract linguistic uncertainty measures at the sentence level, separately for the presentation section (prepared remarks) and the Q\&A section (analyst--management dialogue). We further decompose each transcript by speaker role, distinguishing CEO speech from aggregate management speech. The master manifest contains 112,968 earnings call transcripts. Takeover events for H9 are identified from the SDC Platinum M\&A database, classified as Uninvited (comprising Hostile and Unsolicited bids) or Friendly (comprising Friendly and Neutral bids) and matched to the panel at the firm--quarter level.

\subsection{Samples}
\label{sec:samples}

The raw earnings call universe contains 212,389 transcripts from 6,448 unique firms. Because our CEO-level analyses require executive identification, we merge transcripts with the Execucomp CEO tenure panel by firm--year--month, retaining only calls that match a known CEO record. This step reduces the sample to 115,014 calls (54.2\% match rate), reflecting Execucomp's coverage of S\&P~1500 constituent firms; the 4,643 unmatched firms are predominantly smaller, non-index companies. After further requiring at least five calls per CEO, the master manifest contains 112,968 transcripts. Starting from this manifest, we apply several filters common across our hypothesis suites. We exclude firms in the Finance (Fama--French 12 industry code 11) and Utilities (code 8) sectors, following the convention of omitting regulated and financial industries from corporate governance and market microstructure analyses. For CEO-level specifications, we further restrict to CEOs with at least five observed calls, ensuring meaningful within-CEO variation for the fixed-effects estimator.

The resulting estimation samples vary by hypothesis due to variable availability and listwise deletion of missing observations. The H0.3 replication yields 53,070 observations (Manager Baseline) and 38,671 observations (CEO Baseline), declining modestly to 51,569 and 37,517 in the Extended specifications. The H7 Amihud illiquidity change panel ranges from 38,214 (CEO clarity residual) to 78,679 (Manager QA) observations. The H14 bid-ask spread panel ranges from 38,218 (CEO clarity residual) to 55,485 (Manager presentation) observations. All H14 specifications include \textit{AbsSurpDec} ($|\text{SurpDec}|$, the absolute value of the earnings surprise decile rank) as a control, which has 69.8\% coverage in the Main panel. We construct \textit{AbsSurpDec} from IBES Detail consensus estimates matched via fiscal period end date (\textit{fpedats}) with a 120-day backward tolerance, requiring a minimum of two analysts and $|\text{MEANEST}| \geq 0.05$. The H9 takeover panel contains up to 54,981 firm--quarter intervals, with 307 takeover events in the CEO clarity variant (250 friendly, 40 uninvited, 17 unclassified). Event counts vary by variant due to the availability of clarity residuals (CEO Residual: 275 events; Manager Residual: 354 events).

\subsection{Variable Measurement}
\label{sec:variables}

\paragraph{Linguistic Uncertainty Measures.}
Following Dzielinski et al.\ (2017), we measure linguistic uncertainty as the percentage of words in an earnings call segment that are classified as uncertain by the Loughran--McDonald (LM) financial dictionary. Specifically, for a given segment $s$, $\text{Uncertainty\_pct}_s = 100 \times (\text{LM Uncertainty words in } s) / (\text{total words in } s)$. We compute this separately for the presentation section and the Q\&A section, and for CEO speech versus aggregate management speech, yielding four raw variants: \textit{CEO\_ QA\_ Uncertainty\_ pct}, \textit{CEO\_ Pres\_ Uncertainty\_ pct}, \textit{Manager\_ QA\_ Uncertainty\_ pct}, and \textit{Manager\_ Pres\_ Uncertainty\_ pct}. \textit{Analyst\_ QA\_ Uncertainty\_ pct} captures the percentage of LM uncertainty words spoken by analysts during Q\&A. All linguistic percentage variables are winsorized at the 99th percentile (upper-only) within each calendar year; no lower-bound winsorization is applied because these variables have a natural floor at zero (segments with no uncertain words).

\paragraph{Clarity Scores and Residuals.}
\textit{ClarityCEO} is the negative of the CEO fixed effect ($-\hat{\gamma}_i$) estimated in the H0.3 first-stage regression, standardized to zero mean and unit variance within each industry sample (Main, Finance, Utility). Higher values indicate CEOs who speak with less uncertainty conditional on firm and call characteristics.

\textit{CEO\_ Clarity\_ Residual} and \textit{Manager\_ Clarity\_ Residual} are the call-level residuals from regressing QA-section uncertainty on its linguistic determinants (\textit{Manager\_ Pres\_ Uncertainty\_ pct}/\textit{CEO\_ Pres\_ Uncertainty\_ pct}, \textit{Analyst\_ QA\_ Uncertainty\_ pct}, \textit{Entire\_ All\_ Negative\_ pct}), financial controls, and CEO and year fixed effects. These residuals capture the component of QA uncertainty that is unexplained by observable linguistic, firm-level, and individual-level factors.

\paragraph{Market Illiquidity Measures.}
Both H7 and H14 employ an event-study design with symmetric $\pm$3 trading-day windows around the earnings call. \textit{delta\_amihud} is the change in Amihud (2002) illiquidity around the call: $\overline{A}_{[+1,+3]} - \overline{A}_{[-3,-1]}$, where daily Amihud illiquidity is $A_t = 10^6 \times |r_t| / (\text{VOL}_t \times |\text{PRC}_t|)$ using CRSP daily data (minimum 2 valid trading days per window). Trading-day positions are computed by rank rather than calendar days to handle weekends and holidays. \textit{pre\_call\_amihud} (the pre-window average $\overline{A}_{[-3,-1]}$) enters as a control variable. \textit{delta\_spread} is defined analogously as $\overline{S}_{[+1,+3]} - \overline{S}_{[-3,-1]}$, where the daily spread is $S_t = 2(\text{ASKHI}_t - \text{BIDLO}_t) / (\text{ASKHI}_t + \text{BIDLO}_t)$ from CRSP quote data (minimum 2 valid days per window).

\paragraph{Takeover Indicator.}
\textit{Takeover} equals one in the firm--quarter in which a takeover bid is announced, with separate indicators \textit{Takeover\_Uninvited} and \textit{Takeover\_Friendly}. Following a counting-process format, each firm--quarter contributes an interval at risk until the event or censoring.

\paragraph{Negative Sentiment.}
\textit{Entire\_All\_Negative\_pct} is the percentage of words in the entire call classified as negative by the Loughran--McDonald dictionary: $100 \times (\text{LM Negative words}) / (\text{total words})$, winsorized at 99\% (upper-only) per year.

A comprehensive list of all variable definitions and formulas appears in Appendix~\ref{sec:app_vardef}.

\subsection{Findings}
\label{sec:findings}

\subsubsection{Replication of Dzielinski et al.\ (H0.3)}
\label{sec:h03}

Table~\ref{tab:h03} reports OLS estimates of QA-section uncertainty on \textit{Manager\_ Pres\_ Uncertainty\_ pct}/\textit{CEO\_ Pres\_ Uncertainty\_ pct}, \textit{Analyst\_ QA\_ Uncertainty\_ pct}, \textit{Entire\_ All\_ Negative\_ pct}, and financial controls, with CEO and year fixed effects and CEO-clustered standard errors.

The Baseline specifications replicate the original Dzielinski et al.\ (2017) model. In the Manager variant ($N = 53{,}070$, $R^2 = 0.418$), \textit{Manager\_Pres\_Uncertainty\_pct} enters with a coefficient of 0.096 ($p < 0.001$), \textit{Analyst\_QA\_Uncertainty\_pct} at 0.033 ($p < 0.001$), and \textit{Entire\_All\_Negative\_pct} at 0.077 ($p < 0.001$). The CEO variant ($N = 38{,}671$, $R^2 = 0.372$) yields similar magnitudes: \textit{CEO\_Pres\_Uncertainty\_pct} at 0.093, \textit{Analyst\_QA\_Uncertainty\_pct} at 0.033, and \textit{Entire\_All\_Negative\_pct} at 0.062 (all $p < 0.001$). [Placeholder: comparison with original paper coefficients.]

The Extended specifications add seven firm-level controls---\textit{Size}, \textit{BM}, \textit{Lev}, \textit{ROA}, \textit{CurrentRatio}, \textit{RD\_Intensity}, and \textit{Volatility}---to test the robustness of the baseline associations. In the Manager Extended model ($N = 51{,}569$, $R^2 = 0.420$), the core linguistic coefficients remain virtually unchanged: \textit{Manager\_Pres\_Uncertainty\_pct} at 0.097, \textit{Analyst\_QA\_Uncertainty\_pct} at 0.033, and \textit{Entire\_All\_Negative\_pct} at 0.079 (all $p < 0.001$). Among the extended controls, \textit{ROA} (0.005, $p = 0.047$) and \textit{Volatility} (0.006, $p = 0.007$) are statistically significant, and \textit{CurrentRatio} (0.005, $p = 0.062$) is marginally so, while \textit{Lev}, \textit{Size}, \textit{BM}, and \textit{RD\_Intensity} are not. Of the base controls, \textit{EPS\_Growth} ($p = 0.049$ in the Baseline) loses significance in the Extended specification ($p = 0.245$). The CEO Extended model ($N = 37{,}517$, $R^2 = 0.372$) tells a similar story: \textit{CEO\_Pres\_Uncertainty\_pct} remains at 0.095 ($p < 0.001$), and among extended controls only \textit{ROA} (0.008, $p = 0.012$) reaches significance. The stability of the core coefficients across the baseline and extended specifications indicates that the Dzielinski et al.\ (2017) findings are robust to an enriched control set.

\subsubsection{Uncertainty and Market Illiquidity (H7 \& H14)}
\label{sec:h7h14}

We test whether linguistic uncertainty in earnings calls increases post-call stock illiquidity, using two event-study measures: \textit{delta\_amihud} (H7) and \textit{delta\_spread} (H14), both computed over $\pm$3 trading-day windows around the call. All H7 and H14 $p$-values are one-tailed in the predicted direction ($\beta > 0$).

\paragraph{\textit{delta\_amihud} (H7).}
Table~\ref{tab:h7} reports panel fixed-effects regressions of \textit{delta\_amihud} (post-call minus pre-call Amihud illiquidity) on uncertainty variants, with firm and fiscal-quarter fixed effects and firm-clustered standard errors. Across seven specifications, no uncertainty measure reaches statistical significance at the 5\% level. The strongest signal comes from \textit{Manager\_QA\_Uncertainty\_pct} in Model A3 ($\beta = 0.329$, $p = 0.069$), which is directionally consistent with the hypothesis---higher uncertainty in the Q\&A section is associated with a modest increase in illiquidity---but does not reach conventional significance. \textit{Manager\_Pres\_Uncertainty\_pct} ($\beta = 0.110$, $p = 0.135$) is likewise positive but insignificant. The CEO-level variants are negative and far from significance: \textit{CEO\_QA\_Uncertainty\_pct} ($\beta = -0.063$, $p = 0.814$) and \textit{CEO\_Pres\_Uncertainty\_pct} ($\beta = -0.023$, $p = 0.769$). In Model A5, which includes both manager variants simultaneously, the joint Wald test is marginally significant ($\chi^2 = 2.757$, $p = 0.097$), though neither individual coefficient is significant. The clarity-residual models are likewise null: \textit{CEO\_Clarity\_Residual} ($\beta = 0.015$, $p = 0.165$) and \textit{Manager\_Clarity\_Residual} ($\beta = 0.007$, $p = 0.080$)---both directionally positive but insignificant.

Among control variables, \textit{pre\_call\_amihud} is significant in the manager-level and clarity-residual specifications, with a positive coefficient in the manager variants ($\beta \approx 1.09$, $p = 0.016$) and a negative coefficient in the residual variants ($\beta \approx -0.71$ to $-0.79$, $p < 0.001$), consistent with mean-reversion dynamics in the Amihud measure. \textit{Size} reaches significance in both B1 and B2, and \textit{ROA} is significant in B2 ($p = 0.012$) and marginally so in B1 ($p = 0.064$), but neither reaches significance in the raw uncertainty specifications (A1--A5), where within-$R^2$ is very low (0.001--0.012).

\paragraph{\textit{delta\_spread} (H14).}
Table~\ref{tab:h14} reports panel fixed-effects regressions of \textit{delta\_spread} on the same uncertainty variants, with firm and year--quarter fixed effects and firm-clustered standard errors. Of six primary specifications, one reaches statistical significance: \textit{CEO\_Pres\_Uncertainty\_pct} ($\beta = 0.0004$, $p = 0.024$), indicating that a one-standard-deviation increase in CEO presentation uncertainty is associated with a 0.71\% standard-deviation increase in the bid-ask spread change---a small but statistically detectable effect. The remaining five specifications are insignificant: \textit{Manager\_QA\_Uncertainty\_pct} ($\beta = 0.0001$, $p = 0.353$), \textit{CEO\_QA\_Uncertainty\_pct} ($\beta = 0.0000$, $p = 0.421$), \textit{Manager\_Pres\_Uncertainty\_pct} ($\beta = 0.0002$, $p = 0.223$), \textit{Manager\_Clarity\_Residual} ($\beta = 0.0000$, $p = 0.418$), and \textit{CEO\_Clarity\_Residual} ($\beta = 0.0001$, $p = 0.396$). Controls---particularly \textit{PreCallSpread} ($\beta \approx -0.70$), \textit{Turnover}, \textit{StockPrice}, \textit{Volatility}, and \textit{AbsSurpDec}---dominate the explained variation ($R^2$ ranges from 0.457 to 0.466), indicating that the model captures spread dynamics well.

Taken together, the H7 and H14 results provide limited support for the hypothesis that uncertainty in earnings call speech increases market illiquidity. The strongest H7 signal (\textit{Manager\_QA\_Uncertainty\_pct}, $p = 0.069$) is directionally consistent with the hypothesis but does not reach conventional significance. The sole significant H14 coefficient (\textit{CEO\_Pres\_Uncertainty\_pct}) is economically small. We note that the event-study design ($\pm$3 trading days) is well-suited to isolate call-level information effects; the absence of significant results is unlikely to reflect window-length misspecification.

\subsubsection{Uncertainty and Takeover Likelihood (H9)}
\label{sec:h9}

Table~\ref{tab:h9} reports hazard ratios from Cox proportional hazards models with time-varying covariates and robust sandwich standard errors. We estimate nine sparse-specification models: three event types (\textit{Takeover}, \textit{Takeover\_Uninvited}, \textit{Takeover\_Friendly}) crossed with three clarity variants (\textit{ClarityCEO}, \textit{CEO\_Clarity\_Residual}, \textit{Manager\_Clarity\_Residual}).

The results are uniformly null. For all takeovers, \textit{ClarityCEO} yields a hazard ratio of 0.997 ($p = 0.964$), meaning a one-unit increase in clarity is associated with essentially no change in takeover hazard. \textit{CEO\_Clarity\_Residual} HR $= 1.110$ ($p = 0.600$) and \textit{Manager\_Clarity\_Residual} HR $= 0.940$ ($p = 0.787$)---neither approaching significance.

The cause-specific models for uninvited takeovers, which are of particular theoretical interest as they may proxy for external discipline imposed on uncertain management, are equally null: \textit{ClarityCEO} HR $= 1.112$ ($p = 0.529$), \textit{CEO\_Clarity\_Residual} HR $= 1.002$ ($p = 0.997$), \textit{Manager\_Clarity\_Residual} HR $= 1.339$ ($p = 0.646$). We note that the uninvited-takeover sample is small (36--46 events depending on variant), limiting statistical power, though the point estimates are also economically modest.

For friendly takeovers (224--289 events), the pattern is the same: \textit{ClarityCEO} HR $= 1.008$ ($p = 0.908$), \textit{CEO\_Clarity\_Residual} HR $= 1.127$ ($p = 0.584$), \textit{Manager\_Clarity\_Residual} HR $= 0.902$ ($p = 0.679$).

In sum, we find no evidence that linguistic uncertainty in earnings calls predicts takeover likelihood, whether measured via \textit{ClarityCEO} or as a clarity residual, and regardless of event type. The hypothesis that uncertain speech signals managerial quality problems that attract takeover interest receives no empirical support in our data.

% ============================================================
% IV. ADDITIONAL ANALYSES
% ============================================================
\section{Additional Analyses}
\label{sec:additional}

[Placeholder for additional analyses.]

% ============================================================
% V. CONCLUSION
% ============================================================
\section{Conclusion}
\label{sec:conclusion}

[Placeholder for conclusion.]

% ============================================================
% VI. APPENDIX
% ============================================================
\clearpage
\appendix
\begin{landscape}
\section{Appendix}
\label{sec:appendix}

\subsection{Variable Definitions}
\label{sec:app_vardef}

\begingroup\scriptsize
\begin{longtable}{L{3.8cm} L{1.8cm} L{8.5cm} L{8.5cm}}
\caption{Variable Definitions} \label{tab:vardef} \\
\toprule
\textbf{Variable} & \textbf{Suites} & \textbf{Formula} & \textbf{Description} \\
\midrule
\endfirsthead
\toprule
\textbf{Variable} & \textbf{Suites} & \textbf{Formula} & \textbf{Description} \\
\midrule
\endhead
\bottomrule
\endfoot

\multicolumn{4}{l}{\textit{Panel A: Dependent Variables}} \\
\midrule
Manager\_QA\_Uncertainty\_pct & H0.3 & $100 \times (\text{LM Uncertainty words in Manager Q\&A}) / (\text{total Manager Q\&A words})$ & Percentage of uncertain words spoken by all managers during the Q\&A section of earnings calls, based on the Loughran--McDonald dictionary. Winsorized at 99th percentile (upper-only) per year. \\
CEO\_QA\_Uncertainty\_pct & H0.3 & $100 \times (\text{LM Uncertainty words in CEO Q\&A}) / (\text{total CEO Q\&A words})$ & Percentage of uncertain words spoken by the CEO during the Q\&A section of earnings calls, based on the Loughran--McDonald dictionary. Winsorized at 99th percentile (upper-only) per year. \\
delta\_amihud & H7 & $\overline{A}_{[+1,+3]} - \overline{A}_{[-3,-1]}$; \quad $A_t = 10^6 \times |r_t| / (\text{VOL}_t \times |\text{PRC}_t|)$ & Change in stock illiquidity around the earnings call: average Amihud illiquidity in the 3 trading days after the call minus the 3 trading days before. Positive values indicate worsening liquidity. From CRSP daily data; min 2 valid days per window. \\
delta\_spread & H14 & $\overline{S}_{[+1,+3]} - \overline{S}_{[-3,-1]}$; \quad $S_t = 2(\text{ASKHI} - \text{BIDLO}) / (\text{ASKHI} + \text{BIDLO})$ & Change in the bid-ask spread around the earnings call: average high-low spread in the 3 trading days after minus 3 days before. Positive values indicate widening spreads. From CRSP quote data; min 2 valid days per window. \\
Takeover & H9 & $=1$ in firm--quarter with takeover bid & Indicator equal to one if the firm receives a takeover bid announcement in the quarter. Source: SDC Platinum M\&A database. \\
Takeover\_Uninvited & H9 & $=1$ if bid attitude is Hostile or Unsolicited & Indicator for hostile or unsolicited takeover bids, classified by SDC deal attitude. \\
Takeover\_Friendly & H9 & $=1$ if bid attitude is Friendly or Neutral & Indicator for friendly or neutral takeover bids, classified by SDC deal attitude. \\
\midrule

\multicolumn{4}{l}{\textit{Panel B: Key Independent Variables}} \\
\midrule
Manager\_Pres\_Uncertainty\_pct & H0.3, H7, H14 & $100 \times (\text{LM Uncertainty words in Manager Pres}) / (\text{total Manager Pres words})$ & Percentage of uncertain words spoken by all managers during the prepared presentation section of earnings calls. Winsorized at 99th percentile (upper-only) per year. \\
CEO\_Pres\_Uncertainty\_pct & H0.3, H7, H14 & $100 \times (\text{LM Uncertainty words in CEO Pres}) / (\text{total CEO Pres words})$ & Percentage of uncertain words spoken by the CEO during the prepared presentation section of earnings calls. Winsorized at 99th percentile (upper-only) per year. \\
Analyst\_QA\_Uncertainty\_pct & H0.3, H7 & $100 \times (\text{LM Uncertainty words in Analyst Q\&A}) / (\text{total Analyst Q\&A words})$ & Percentage of uncertain words spoken by analysts during the Q\&A section. Captures the uncertainty in questions posed to management. Winsorized at 99th percentile (upper-only) per year. \\
Entire\_All\_Negative\_pct & H0.3, H7 & $100 \times (\text{LM Negative words in entire call}) / (\text{total words in entire call})$ & Percentage of negative-sentiment words in the entire earnings call transcript, based on the Loughran--McDonald dictionary. Winsorized at 99th percentile (upper-only) per year. \\
ClarityCEO & H9 & $-\hat{\gamma}_i$ from H0.3 CEO FE regression & Standardized CEO-level clarity score derived from fixed effects. Higher values indicate CEOs who consistently speak with less uncertainty after controlling for firm and call characteristics. z-scored within each industry sample. \\
CEO\_Clarity\_Residual & H7, H9, H14 & $\hat{u}_{it}$ from H0.3 CEO Extended regression & Call-level unexplained uncertainty: the component of CEO Q\&A uncertainty not attributable to presentation uncertainty, analyst uncertainty, negative sentiment, financial controls, or CEO and year fixed effects. \\
Manager\_Clarity\_Residual & H7, H9, H14 & $\hat{u}_{it}$ from H0.3 Manager Extended regression & Call-level unexplained uncertainty: the component of manager Q\&A uncertainty not attributable to presentation uncertainty, analyst uncertainty, negative sentiment, financial controls, or CEO and year fixed effects. \\
\midrule

\multicolumn{4}{l}{\textit{Panel C: Financial Controls}} \\
\midrule
Size & All & $\ln(\texttt{atq})$ where $\texttt{atq} > 0$ & Natural logarithm of total assets, measuring firm size. From Compustat quarterly. \\
BM & H0.3, H9 & $\texttt{ceqq} / (\texttt{cshoq} \times \texttt{prccq})$ & Book-to-market ratio: book equity divided by market capitalization. Measures relative valuation; higher values indicate cheaper (value) firms. From Compustat quarterly. \\
Lev & All & $(\texttt{dlcq} + \texttt{dlttq}) / \texttt{atq}$ & Financial leverage: interest-bearing debt (short-term + long-term) as a fraction of total assets. Missing debt items filled as zero. From Compustat quarterly. \\
ROA & All & $\texttt{iby} / \overline{\texttt{atq}}$; \quad $\overline{\texttt{atq}} = (\texttt{atq}_t + \texttt{atq}_{t-1})/2$ & Return on assets: annual income before extraordinary items divided by average total assets. Measures firm profitability. From Compustat. \\
CurrentRatio & H0.3 & $\texttt{actq} / \texttt{lctq}$ & Current ratio: current assets divided by current liabilities. Measures short-term liquidity and ability to meet near-term obligations. From Compustat quarterly. \\
RD\_Intensity & H0.3 & $\texttt{xrdq} / \texttt{atq}$ & Research and development intensity: quarterly R\&D expenditure as a fraction of total assets. Missing R\&D filled as zero. From Compustat quarterly. \\
Volatility & H0.3, H14 & $\text{std}(r_t) \times \sqrt{252} \times 100$ & Annualized stock return volatility computed over the inter-call window (from one call to the next, excluding 5 days before the next call). Minimum 10 trading days required. From CRSP daily returns. \\
StockRet & H0.3 & $(\prod(1 + r_t) - 1) \times 100$ & Cumulative stock return over the inter-call window, expressed as a percentage. Minimum 10 trading days required. From CRSP daily returns. \\
MarketRet & H0.3 & $(\prod(1 + \texttt{VWRETD}_t) - 1) \times 100$ & Cumulative value-weighted market return over the same inter-call window as StockRet. Controls for broad market movements. Minimum 10 trading days required. From CRSP. \\
EPS\_Growth & H0.3 & $(\texttt{epspxq}_t - \texttt{epspxq}_{t-4}) / |\texttt{epspxq}_{t-4}|$ & Year-over-year growth in earnings per share (excluding extraordinary items). Lag matched by date with $\pm 45$-day tolerance. From Compustat quarterly. \\
SurpDec & H0.3 & Signed surprise rank $\in [-5, +5]$ & Earnings surprise decile: analyst forecast errors ranked within each quarter and mapped to an ordinal scale from $-5$ (largest negative surprise) to $+5$ (largest positive surprise). From IBES Detail. \\
TobinsQ & H7 & $(\texttt{cshoq} \times \texttt{prccq} + \texttt{dlcq} + \texttt{dlttq}) / \texttt{atq}$ & Tobin's Q: market value of equity plus interest-bearing debt, divided by total assets. Measures growth opportunities and market valuation relative to replacement cost. From Compustat quarterly. \\
pre\_call\_amihud & H7 & $\overline{A}_{[-3,-1]}$ & Average Amihud illiquidity in the 3 trading days before the earnings call. Controls for the firm's baseline liquidity level. \\
CashHoldings & H9 & $\texttt{cheq} / \texttt{atq}$ & Cash holdings: cash and short-term investments as a fraction of total assets. From Compustat quarterly. \\
StockPrice & H14 & $|\texttt{PRC}|$ on or before call date & Closing stock price on the earnings call date or nearest prior trading day. Higher-priced stocks tend to have tighter spreads. From CRSP daily. \\
Turnover & H14 & $\texttt{VOL} / (\texttt{SHROUT} \times 1000)$ & Share turnover: daily trading volume as a fraction of shares outstanding on the call date. Measures baseline trading activity. From CRSP daily. \\
PreCallSpread & H14 & $2(\text{ASKHI} - \text{BIDLO}) / (\text{ASKHI} + \text{BIDLO})$ & Average bid-ask spread in the 3 trading days before the earnings call. Controls for the firm's baseline spread level. Minimum 2 valid days. From CRSP. \\
AbsSurpDec & H0.3, H14 & $|\text{SurpDec}|$ (ordinal 0--5) & Absolute earnings surprise magnitude: the unsigned version of SurpDec, measuring how much actual earnings deviated from analyst expectations regardless of direction. From IBES Detail consensus matched via fiscal period end date ($\pm 120$d), requiring $\geq 2$ analysts. \\
\end{longtable}
\endgroup
\end{landscape}

% --- Unified Summary Statistics ---
\begin{landscape}
\subsection{Summary Statistics}
\label{sec:app_sumstats}
\begingroup\scriptsize
\begin{longtable}{@{}lrrrrrrrr@{}}
\caption{Unified Summary Statistics --- All Variables Across Suites} \label{tab:sumstats} \\
\toprule
Variable & $N$ & Mean & SD & Min & P25 & Median & P75 & Max \\
\midrule
\endfirsthead
\toprule
Variable & $N$ & Mean & SD & Min & P25 & Median & P75 & Max \\
\midrule
\endhead
\bottomrule
\endfoot

\multicolumn{9}{@{}l}{\textit{Panel A: Dependent Variables}} \\
\midrule
Manager\_QA\_Uncertainty\_pct & 84,484 & 0.821 & 0.321 & 0.000 & 0.599 & 0.792 & 1.009 & 2.037 \\
CEO\_QA\_Uncertainty\_pct & 62,132 & 0.777 & 0.391 & 0.000 & 0.512 & 0.738 & 0.998 & 2.514 \\
delta\_amihud & 86,906 & 0.092 & 12.624 & $-99.595$ & $-0.001$ & $-0.000$ & 0.000 & 2678.235 \\
delta\_spread & 87,157 & $-0.004$ & 0.022 & $-0.586$ & $-0.013$ & $-0.003$ & 0.005 & 1.167 \\
Takeover & 84,104 & 0.007 & 0.081 & 0.000 & 0.000 & 0.000 & 0.000 & 1.000 \\
Takeover\_Uninvited & 84,104 & 0.001 & 0.029 & 0.000 & 0.000 & 0.000 & 0.000 & 1.000 \\
Takeover\_Friendly & 84,104 & 0.006 & 0.074 & 0.000 & 0.000 & 0.000 & 0.000 & 1.000 \\
\midrule

\multicolumn{9}{@{}l}{\textit{Panel B: Key Independent Variables}} \\
\midrule
Manager\_Pres\_Uncertainty\_pct & 86,038 & 0.863 & 0.353 & 0.000 & 0.613 & 0.822 & 1.066 & 2.096 \\
CEO\_Pres\_Uncertainty\_pct & 62,049 & 0.656 & 0.390 & 0.000 & 0.377 & 0.596 & 0.867 & 2.233 \\
Analyst\_QA\_Uncertainty\_pct & 81,031 & 1.440 & 0.483 & 0.000 & 1.122 & 1.411 & 1.727 & 3.595 \\
Entire\_All\_Negative\_pct & 86,858 & 0.921 & 0.302 & 0.000 & 0.704 & 0.880 & 1.094 & 2.390 \\
ClarityCEO & 52,080 & $-0.074$ & 0.975 & $-4.505$ & $-0.618$ & 0.019 & 0.608 & 3.270 \\
CEO\_Clarity\_Residual & 38,671 & 0.000 & 0.299 & $-1.514$ & $-0.184$ & $-0.017$ & 0.164 & 1.763 \\
Manager\_Clarity\_Residual & 53,070 & 0.000 & 0.235 & $-1.295$ & $-0.153$ & $-0.011$ & 0.141 & 1.293 \\
\midrule

\multicolumn{9}{@{}l}{\textit{Panel C: Financial Controls}} \\
\midrule
Size & 87,994 & 7.471 & 1.661 & $-0.569$ & 6.301 & 7.376 & 8.544 & 12.459 \\
BM & 83,443 & 0.458 & 0.583 & $-20.775$ & 0.231 & 0.389 & 0.617 & 7.858 \\
Lev & 87,994 & 0.233 & 0.224 & 0.000 & 0.047 & 0.207 & 0.346 & 3.945 \\
ROA & 87,552 & 0.039 & 0.133 & $-3.983$ & 0.015 & 0.053 & 0.093 & 0.549 \\
CurrentRatio & 85,783 & 2.556 & 2.149 & 0.070 & 1.377 & 1.988 & 2.973 & 46.411 \\
RD\_Intensity & 87,994 & 0.010 & 0.021 & 0.000 & 0.000 & 0.000 & 0.013 & 0.405 \\
Volatility & 82,599 & 36.756 & 21.244 & 9.439 & 22.971 & 31.276 & 43.815 & 211.916 \\
StockRet & 82,599 & 3.067 & 18.619 & $-74.041$ & $-6.806$ & 2.832 & 12.214 & 142.666 \\
MarketRet & 82,599 & 2.213 & 7.601 & $-36.285$ & $-1.332$ & 3.519 & 6.744 & 30.678 \\
EPS\_Growth & 86,535 & 0.123 & 3.093 & $-36.830$ & $-0.319$ & 0.111 & 0.601 & 16.144 \\
SurpDec & 61,544 & 1.209 & 3.026 & $-5.000$ & $-1.000$ & 2.000 & 4.000 & 5.000 \\
TobinsQ & 86,781 & 1.829 & 1.508 & 0.082 & 0.960 & 1.386 & 2.143 & 35.413 \\
pre\_call\_amihud & 86,906 & 0.044 & 1.380 & 0.000 & 0.000 & 0.001 & 0.004 & 267.826 \\
CashHoldings & 83,930 & 0.171 & 0.181 & 0.000 & 0.037 & 0.105 & 0.245 & 0.994 \\
StockPrice & 87,188 & 38.694 & 51.720 & 0.035 & 14.898 & 28.240 & 48.170 & 2080.020 \\
Turnover & 87,188 & 0.027 & 0.042 & 0.000 & 0.008 & 0.016 & 0.031 & 3.773 \\
PreCallSpread & 87,157 & 0.042 & 0.027 & 0.000 & 0.025 & 0.036 & 0.051 & 0.733 \\
AbsSurpDec & 61,544 & 2.930 & 1.426 & 0 & 2 & 3 & 4 & 5 \\
\\[-6pt]
\multicolumn{9}{@{}l}{\textit{Note:} Summary statistics computed on the Main sample ($N = 88{,}205$).} \\
\end{longtable}
\endgroup
\end{landscape}

% ===== TABLE A.1: H0.3 =====
\begin{table}[H]
\centering
\caption{H0.3 --- Replication and Extended Controls Robustness of Dzielinski et al.}
\label{tab:h03}
\begin{threeparttable}
\begin{scriptsize}
\renewcommand{\arraystretch}{0.75}
\begin{tabular}{lcccc}
\toprule
& \multicolumn{2}{c}{DV: Manager\_QA\_Uncertainty\_pct} & \multicolumn{2}{c}{DV: CEO\_QA\_Uncertainty\_pct} \\
\cmidrule(lr){2-3} \cmidrule(lr){4-5}
& (1) Baseline & (2) Extended & (3) Baseline & (4) Extended \\
\midrule
\textit{Linguistic Variables} \\
Manager\_Pres\_Uncertainty\_pct / CEO\_Pres\_Uncertainty\_pct & \textbf{0.0960}$^{***}$ & \textbf{0.0970}$^{***}$ & \textbf{0.0930}$^{***}$ & \textbf{0.0950}$^{***}$ \\
 & (0.006) & (0.006) & (0.007) & (0.007) \\
Analyst\_QA\_Uncertainty\_pct & \textbf{0.0330}$^{***}$ & \textbf{0.0330}$^{***}$ & \textbf{0.0330}$^{***}$ & \textbf{0.0340}$^{***}$ \\
 & (0.003) & (0.003) & (0.004) & (0.004) \\
Entire\_All\_Negative\_pct & \textbf{0.0770}$^{***}$ & \textbf{0.0790}$^{***}$ & \textbf{0.0620}$^{***}$ & \textbf{0.0680}$^{***}$ \\
 & (0.006) & (0.006) & (0.009) & (0.009) \\
\textit{Base Controls} \\
StockRet & 0.0000 & 0.0010 & 0.0020 & 0.0020 \\
 & (0.001) & (0.001) & (0.002) & (0.002) \\
MarketRet & 0.0010 & 0.0020 & $\mathbf{-0.0040}^{*}$ & $-0.0030$ \\
 & (0.002) & (0.002) & (0.002) & (0.002) \\
EPS\_Growth & \textbf{0.0020}$^{**}$ & 0.0010 & 0.0020 & 0.0000 \\
 & (0.001) & (0.001) & (0.002) & (0.002) \\
SurpDec & \textbf{0.0040}$^{***}$ & \textbf{0.0040}$^{***}$ & 0.0030 & 0.0020 \\
 & (0.001) & (0.001) & (0.002) & (0.002) \\
\textit{Extended Controls} \\
Size & & 0.0000 & & 0.0020 \\
 & & (0.010) & & (0.013) \\
BM & & $-0.0030$ & & $-0.0030$ \\
 & & (0.003) & & (0.004) \\
Lev & & $-0.0060$ & & $-0.0090$ \\
 & & (0.004) & & (0.006) \\
ROA & & \textbf{0.0050}$^{**}$ & & \textbf{0.0080}$^{**}$ \\
 & & (0.002) & & (0.003) \\
CurrentRatio & & \textbf{0.0050}$^{*}$ & & 0.0030 \\
 & & (0.003) & & (0.004) \\
RD\_Intensity & & 0.0000 & & 0.0050 \\
 & & (0.004) & & (0.004) \\
Volatility & & \textbf{0.0060}$^{***}$ & & 0.0040 \\
 & & (0.002) & & (0.003) \\
\midrule
CEO FE & Yes & Yes & Yes & Yes \\
Year FE & Yes & Yes & Yes & Yes \\
SE Cluster & CEO & CEO & CEO & CEO \\
$N$ & 53,070 & 51,569 & 38,671 & 37,517 \\
$R^2$ & 0.418 & 0.420 & 0.372 & 0.372 \\
Adj.\ $R^2$ & 0.389 & 0.392 & 0.339 & 0.338 \\
\bottomrule
\end{tabular}
\end{scriptsize}
\begin{tablenotes}[flushleft]
\footnotesize
\item \textit{Notes:} $^{***}p<0.01$, $^{**}p<0.05$, $^{*}p<0.10$. Standard errors clustered at CEO level in parentheses. Cols (1)--(2) use Manager\_Pres\_Uncertainty\_pct; cols (3)--(4) use CEO\_Pres\_Uncertainty\_pct. Baseline models replicate Dzielinski et al.\ (2017); Extended models add firm-level controls. All continuous controls are standardized within each model's estimation sample. Coefficients reflect standardized units.
\end{tablenotes}
\end{threeparttable}
\end{table}

% ===== TABLE A.2: H7 =====
\begin{table}[H]
\centering
\caption{H7 --- Linguistic Uncertainty and Amihud Illiquidity Change}
\label{tab:h7}
\begin{threeparttable}
\begin{scriptsize}
\renewcommand{\arraystretch}{0.85}
\begin{tabular}{lccccccc}
\toprule
& (A1) & (A2) & (A3) & (A4) & (A5) & (B1) & (B2) \\
& CEO QA & CEO Pres & Mgr QA & Mgr Pres & Mgr QA+Pres & CEO Resid & Mgr Resid \\
\midrule
CEO\_QA\_Uncertainty\_pct & $-0.0630$ & & & & & & \\
 & (0.0706) & & & & & & \\[1pt]
CEO\_Pres\_Uncertainty\_pct & & $-0.0229$ & & & & & \\
 & & (0.0310) & & & & & \\[1pt]
Manager\_QA\_Uncertainty\_pct & & & 0.3285 & & 0.3214 & & \\
 & & & (0.2212) & & (0.2143) & & \\[1pt]
Manager\_Pres\_Uncertainty\_pct & & & & 0.1100 & 0.0738 & & \\
 & & & & (0.0998) & (0.0777) & & \\[1pt]
CEO\_Clarity\_Residual & & & & & & 0.0151 & \\
 & & & & & & (0.0155) & \\[1pt]
Manager\_Clarity\_Residual & & & & & & & 0.0072 \\
 & & & & & & & (0.0051) \\[1pt]
Entire\_All\_Negative\_pct & 0.0584 & 0.0585 & $-0.2221$ & $-0.2077$ & $-0.2302$ & $\mathbf{0.0084}^{*}$ & 0.0051 \\
 & (0.0485) & (0.0431) & (0.1944) & (0.1878) & (0.2024) & (0.0044) & (0.0035) \\[1pt]
Analyst\_QA\_Uncertainty\_pct & $-0.0075$ & $-0.0092$ & $-0.3200$ & $-0.3093$ & $-0.3210$ & 0.0035 & 0.0021 \\
 & (0.0101) & (0.0121) & (0.3133) & (0.3075) & (0.3142) & (0.0093) & (0.0065) \\[1pt]
Size & $-0.2207$ & $-0.2234$ & $-0.2772$ & $-0.2798$ & $-0.2790$ & $\mathbf{-0.0174}^{**}$ & $\mathbf{-0.0129}^{**}$ \\
 & (0.1883) & (0.1911) & (0.2164) & (0.2182) & (0.2179) & (0.0085) & (0.0059) \\[1pt]
Lev & $-0.0959$ & $-0.0951$ & 0.5499 & 0.5491 & 0.5536 & $-0.0127$ & $-0.0097$ \\
 & (0.0820) & (0.0805) & (0.6067) & (0.6068) & (0.6094) & (0.0224) & (0.0159) \\[1pt]
ROA & $-0.3775$ & $-0.3794$ & 0.3942 & 0.4185 & 0.3969 & $\mathbf{-0.0642}^{*}$ & $\mathbf{-0.0810}^{**}$ \\
 & (0.3059) & (0.3117) & (0.6895) & (0.7028) & (0.6918) & (0.0346) & (0.0322) \\[1pt]
TobinsQ & $\mathbf{-0.0156}^{*}$ & $\mathbf{-0.0165}^{*}$ & $-0.0379$ & $-0.0371$ & $-0.0382$ & $-0.0019$ & $-0.0011$ \\
 & (0.0089) & (0.0097) & (0.0360) & (0.0356) & (0.0362) & (0.0014) & (0.0010) \\[1pt]
pre\_call\_amihud & $-0.4592$ & $-0.4586$ & $\mathbf{1.0867}^{**}$ & $\mathbf{1.0864}^{**}$ & $\mathbf{1.0867}^{**}$ & $\mathbf{-0.7935}^{***}$ & $\mathbf{-0.7136}^{***}$ \\
 & (0.4124) & (0.4133) & (0.4527) & (0.4530) & (0.4527) & (0.0664) & (0.1009) \\[1pt]
\midrule
Firm FE & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\
Quarter FE & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\
SE Cluster & Firm & Firm & Firm & Firm & Firm & Firm & Firm \\
$N$ & 58,240 & 57,216 & 78,679 & 78,621 & 78,597 & 38,214 & 52,415 \\
Entities & 1,626 & 1,619 & 1,845 & 1,846 & 1,845 & 1,291 & 1,504 \\
$R^2$ (within) & 0.001 & 0.001 & 0.012 & 0.012 & 0.012 & 0.044 & 0.038 \\
\bottomrule
\end{tabular}
\end{scriptsize}
\begin{tablenotes}[flushleft]
\footnotesize
\item \textit{Notes:} $^{***}p<0.01$, $^{**}p<0.05$, $^{*}p<0.10$ (two-tailed). Standard errors clustered at firm level in parentheses. DV: delta\_amihud $= \overline{A}_{[+1,+3]} - \overline{A}_{[-3,-1]}$ (post-call minus pre-call Amihud illiquidity, $\pm$3 trading days). Uncertainty measure per column: (A1) CEO\_QA\_Uncertainty\_pct, (A2) CEO\_Pres\_Uncertainty\_pct, (A3) Manager\_QA\_Uncertainty\_pct, (A4) Manager\_Pres\_Uncertainty\_pct, (A5) both Manager QA and Pres entered simultaneously (Wald $\chi^2 = 2.757$, $p = 0.097$), (B1) CEO\_Clarity\_Residual, (B2) Manager\_Clarity\_Residual. All models include Entire\_All\_Negative\_pct, Analyst\_QA\_Uncertainty\_pct, and pre\_call\_amihud as controls.
\end{tablenotes}
\end{threeparttable}
\end{table}

% ===== TABLE A.3: H14 =====
\begin{table}[H]
\centering
\caption{H14 --- Linguistic Uncertainty and Bid-Ask Spread Change}
\label{tab:h14}
\begin{threeparttable}
\begin{footnotesize}
\renewcommand{\arraystretch}{0.9}
\begin{tabular}{lcccccc}
\toprule
& (1) & (2) & (3) & (4) & (5) & (6) \\
& Mgr QA & CEO QA & Mgr Pres & CEO Pres & Mgr Resid & CEO Resid \\
\midrule
Uncertainty measure & 0.0001 & 0.0000 & 0.0002 & $\mathbf{0.0004}^{**}$ & 0.0000 & 0.0001 \\
(see column header) & (0.0002) & (0.0002) & (0.0002) & (0.0002) & (0.0002) & (0.0002) \\
 & [$p=0.353$] & [$p=0.421$] & [$p=0.223$] & [$p=0.024$] & [$p=0.418$] & [$p=0.396$] \\[1pt]
Size & $\mathbf{-0.0009}^{***}$ & $\mathbf{-0.0010}^{***}$ & $\mathbf{-0.0009}^{***}$ & $\mathbf{-0.0010}^{***}$ & $\mathbf{-0.0008}^{***}$ & $\mathbf{-0.0009}^{***}$ \\
 & (0.0002) & (0.0003) & (0.0002) & (0.0003) & (0.0002) & (0.0003) \\[1pt]
StockPrice & $\mathbf{-0.0000}^{***}$ & $\mathbf{-0.0000}^{***}$ & $\mathbf{-0.0000}^{***}$ & $\mathbf{-0.0000}^{***}$ & $\mathbf{-0.0000}^{***}$ & $\mathbf{-0.0000}^{***}$ \\
 & (0.0000) & (0.0000) & (0.0000) & (0.0000) & (0.0000) & (0.0000) \\[1pt]
Turnover & \textbf{0.0710}$^{***}$ & \textbf{0.0683}$^{***}$ & \textbf{0.0705}$^{***}$ & \textbf{0.0675}$^{***}$ & \textbf{0.0690}$^{***}$ & \textbf{0.0654}$^{***}$ \\
 & (0.0037) & (0.0040) & (0.0037) & (0.0041) & (0.0035) & (0.0039) \\[1pt]
Volatility & \textbf{0.0005}$^{***}$ & \textbf{0.0005}$^{***}$ & \textbf{0.0005}$^{***}$ & \textbf{0.0005}$^{***}$ & \textbf{0.0005}$^{***}$ & \textbf{0.0005}$^{***}$ \\
 & (0.0000) & (0.0000) & (0.0000) & (0.0000) & (0.0000) & (0.0000) \\[1pt]
PreCallSpread & $\mathbf{-0.6887}^{***}$ & $\mathbf{-0.7010}^{***}$ & $\mathbf{-0.6894}^{***}$ & $\mathbf{-0.7009}^{***}$ & $\mathbf{-0.6919}^{***}$ & $\mathbf{-0.7063}^{***}$ \\
 & (0.0214) & (0.0158) & (0.0211) & (0.0154) & (0.0230) & (0.0165) \\[1pt]
AbsSurpDec & \textbf{0.0002}$^{***}$ & \textbf{0.0002}$^{***}$ & \textbf{0.0002}$^{***}$ & \textbf{0.0002}$^{***}$ & \textbf{0.0002}$^{***}$ & \textbf{0.0002}$^{***}$ \\
 & (0.0001) & (0.0001) & (0.0001) & (0.0001) & (0.0001) & (0.0001) \\[1pt]
\midrule
Firm FE & Yes & Yes & Yes & Yes & Yes & Yes \\
Year--Quarter FE & Yes & Yes & Yes & Yes & Yes & Yes \\
SE Cluster & Firm & Firm & Firm & Firm & Firm & Firm \\
$N$ & 54,726 & 41,289 & 55,485 & 40,986 & 51,972 & 38,218 \\
Entities & 1,534 & 1,332 & 1,541 & 1,331 & 1,509 & 1,298 \\
$R^2$ (within) & 0.457 & 0.462 & 0.457 & 0.462 & 0.462 & 0.466 \\
\bottomrule
\end{tabular}
\end{footnotesize}
\begin{tablenotes}[flushleft]
\footnotesize
\item \textit{Notes:} $^{***}p<0.01$, $^{**}p<0.05$, $^{*}p<0.10$ (one-tailed for uncertainty measure: $\beta > 0$; two-tailed for controls). Standard errors clustered at firm level in parentheses. DV: delta\_spread (post$-$pre call bid-ask spread, $\pm$3 trading days). Sample conditioned on IBES consensus coverage (AbsSurpDec). Uncertainty measure per column: (1) Manager\_QA\_Uncertainty\_pct, (2) CEO\_QA\_Uncertainty\_pct, (3) Manager\_Pres\_Uncertainty\_pct, (4) CEO\_Pres\_Uncertainty\_pct, (5) Manager\_Clarity\_Residual, (6) CEO\_Clarity\_Residual.
\end{tablenotes}
\end{threeparttable}
\end{table}

% ===== TABLE A.4: H9 =====
\begin{table}[H]
\centering
\caption{H9 --- Takeover Hazard Ratios (Cox PH, Sparse Specification)}
\label{tab:h9}
\begin{threeparttable}
\begin{scriptsize}
\renewcommand{\arraystretch}{0.85}
\begin{tabular}{lccccccccc}
\toprule
& \multicolumn{3}{c}{All Takeovers} & \multicolumn{3}{c}{Uninvited} & \multicolumn{3}{c}{Friendly} \\
\cmidrule(lr){2-4} \cmidrule(lr){5-7} \cmidrule(lr){8-10}
& CEO & CEO & Mgr & CEO & CEO & Mgr & CEO & CEO & Mgr \\
& Clarity & Resid & Resid & Clarity & Resid & Resid & Clarity & Resid & Resid \\
\midrule
Clarity Measure & 0.997 & 1.110 & 0.940 & 1.112 & 1.002 & 1.339 & 1.008 & 1.127 & 0.902 \\
 & (0.059) & (0.198) & (0.227) & (0.168) & (0.552) & (0.634) & (0.065) & (0.219) & (0.250) \\[1pt]
Size & 0.945 & 0.939 & $\mathbf{0.924}^{**}$ & 1.084 & 1.186 & $\mathbf{1.200}^{*}$ & $\mathbf{0.888}^{***}$ & $\mathbf{0.868}^{***}$ & $\mathbf{0.857}^{***}$ \\
 & (0.041) & (0.044) & (0.038) & (0.108) & (0.116) & (0.098) & (0.046) & (0.050) & (0.043) \\[1pt]
BM & $\mathbf{1.201}^{*}$ & 1.162 & 1.163 & $\mathbf{1.423}^{*}$ & 1.276 & 1.394 & $\mathbf{1.202}^{*}$ & 1.172 & 1.166 \\
 & (0.094) & (0.107) & (0.099) & (0.213) & (0.245) & (0.218) & (0.105) & (0.119) & (0.109) \\[1pt]
Lev & 1.390 & 1.401 & 1.353 & 1.326 & 1.325 & 1.296 & $\mathbf{1.505}^{*}$ & 1.487 & 1.459 \\
 & (0.238) & (0.250) & (0.230) & (0.734) & (0.779) & (0.721) & (0.243) & (0.258) & (0.238) \\[1pt]
ROA & $\mathbf{0.445}^{**}$ & $\mathbf{0.449}^{*}$ & 0.585 & 0.359 & 0.258 & 0.415 & $\mathbf{0.470}^{*}$ & 0.506 & 0.614 \\
 & (0.408) & (0.471) & (0.414) & (1.215) & (1.211) & (1.147) & (0.431) & (0.513) & (0.442) \\[1pt]
CashHoldings & 1.437 & 1.536 & 1.102 & 1.743 & 3.387 & 2.412 & 1.392 & 1.338 & 1.008 \\
 & (0.356) & (0.374) & (0.326) & (1.018) & (1.016) & (0.899) & (0.388) & (0.411) & (0.356) \\[1pt]
\midrule
$N$ intervals & 51,627 & 40,310 & 54,981 & 51,627 & 40,310 & 54,981 & 51,627 & 40,310 & 54,981 \\
Events & 307 & 275 & 354 & 40 & 36 & 46 & 250 & 224 & 289 \\
Concordance & 0.518 & 0.518 & 0.519 & 0.569 & 0.580 & 0.566 & 0.486 & 0.509 & 0.504 \\
\bottomrule
\end{tabular}
\end{scriptsize}
\begin{tablenotes}[flushleft]
\footnotesize
\item \textit{Notes:} $^{***}p<0.01$, $^{**}p<0.05$, $^{*}p<0.10$. Cox proportional hazards models with time-varying covariates in counting-process format. Hazard ratios reported; standard errors of the log-hazard coefficient in parentheses. Uninvited and friendly are cause-specific models (competing events censored). Standard errors are robust sandwich estimators (not firm-clustered). Clarity measure per column: CEO Clarity = ClarityCEO (standardized composite clarity score), CEO Resid = CEO\_Clarity\_Residual, Mgr Resid = Manager\_Clarity\_Residual (both residuals from H0.3 first-stage regression).
\end{tablenotes}
\end{threeparttable}
\end{table}

\end{document}
